Global well-being and mental health in the internet age

### 2022-07-14 Analysis.qmd
Update meta

---
title: Global mental health and well-being in the internet age
description: | 
  Online analysis supplement to "Global mental health and well-being in the internet age (Vuorre & Przybylski, 2022)"
author:
  - name: Matti Vuorre
    affiliation: University of Oxford
    affiliation-url: https://www.oii.ox.ac.uk/people/matti-vuorre/
    orcid_id: 0000-0001-5052-066X
citation:
  url: https://github.com/digital-wellbeing/global-wbmh/
date: 2022-07-06
toc: true
toc-depth: 2
toc-location: left
number-sections: true
format:
  html:
    code-fold: true
    code-summary: "Show the code"
    html-math-method: katex
    theme: pulse
    anchor-sections: true
    self-contained: true
    self-contained-math: false
editor_options: 
  chunk_output_type: inline
---

@@

Welcome! This document is the online analysis supplement to *Global mental health and well-being in the internet age* (Vuorre & Przybylski, [submitted]()). It contains all the analyses reported in the manuscript along with supplemental figures and data. The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).

>>>>

---
title: Global well-being and mental health in the internet age
description: | 
  Online analysis supplement to [*Global well-being and mental health in the internet age*](preprint url) (Vuorre & Przybylski, 2022)
author:
  - name: Matti Vuorre
    affiliation: University of Oxford
    affiliation-url: https://www.oii.ox.ac.uk/people/matti-vuorre/
    orcid_id: 0000-0001-5052-066X
citation:
  url: https://github.com/digital-wellbeing/global-wbmh/
date: 2022-07-06
toc: true
toc-depth: 2
toc-location: left
number-sections: true
format:
  html:
    code-fold: true
    code-summary: "Show the code"
    html-math-method: katex
    theme: pulse
    anchor-sections: true
    self-contained: true
    self-contained-math: false
editor_options: 
  chunk_output_type: console
---

@@

This document is the online analysis supplement to *Global well-being and mental health in the internet age* (Vuorre & Przybylski, [submitted]()). It contains all the analyses reported in the manuscript along with supplemental analyses. The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [Zenodo]().
